% mentioned p.9
\documentclass[10pt|draft]{report}

\usepackage[hidelinks]{hyperref}
\usepackage[]{datetime} 

% mentioned of p.226 of Lamport, 2ed
\ttfamily
\title{Distilling Lamport or \em Red Hen's First Adventure}

\begin{document}

\maketitle
% https://tex.stackexchange.com/questions/319875/how-to-make-dedication-page-and-move-words-to-the-middle
\clearpage
\begin{center}
    \thispagestyle{empty}
    \vspace*{\fill}
    For Rocco
    \vspace*{\fill}
\end{center}
\clearpage

\begin{quote}
{\em\small{Meandering and shallow investigation of \LaTeX{}. The fax. Aspen nights and drones above.}}
\end{quote} 

\begin{verbatim}
% This document starts with:
\documentclass[10pt|draft]{report}
% Next, we write:
\usepackage[hidelinks]{hyperref}
Next, we set the font family like so:
% mentioned of p.226 of Lamport, 2ed
\ttfamily
% and we set the title (% means this is a comment)
\title{Distilling Lamport or \em Red Hen's First Adventure}
% and finally:
\begin{document}

\maketitle

\begin{quote}
{\em\small{Meandering and shallow investigation of \LaTeX{}. The fax. Aspen nights 
and drones above.}}
\end{quote} 

\end{verbatim}

\begin{quote}
One of the hardest things about using \LaTeX{} is deciding how to pronounce it.
\end{quote}

I, for one, pronounce it like the gloves one finds in most hospitals.

What is a \verb|documentclass| anyway? Well, there are some standard classes such as: \verb|article|, \verb|report|, \verb|book|, \verb|letter|, and \verb|slides|.

The \verb|article| class is generally used for shorter documents and \verb|report| for longer (p.19).

``Convention' dictates that punctuation go inside the quotes, like ``this,'' but [Lamport] think[s] it's better to do ``this''.

Lamport does not mention the use of Backtick (`) to get quotes right. Or maybe he does and we missed it. In any case,

\begin{verbatim}
``this'' is how you'd want to write/typeset quotes so they are produced correctly.
\end{verbatim}

If you would like to know more: \url{https://stuff.mit.edu/afs/sipb/project/www/latex/guide/node12.html}. We'll hammer this home in a few milliseconds.

Hammering it home, now:
\begin{verbatim}
Use ` to begin quotation, not ' "
\end{verbatim}

The shorthand for verbatim text is \verb|\verb|. 
Literally written as \texttt{\textbackslash{verb|} \textbackslash{verb|}}.

\begin{verbatim}
Literally written as \texttt{\textbackslash{verb|} \textbackslash{verb|}}.
\end{verbatim}

\section*{}

Red Hen sat at the desk and contemplated firing a few rounds into his head but he knew it was pointless and he begin to wonder why he was programmed at all to allow such thoughts and that thought looped for awhile and meantime he's Martin Riggs staring at the face of his cocked pistol and feeling like a pustule.

Red Hen looked at the desk before him rummaged through and disordered; why was he here again. He'd like to know and even though it was equipped with NPUs and CPUs and God knows what it still never really understood why it acted so human and mostly forgot why it was doing what it was doing and for what reason and what did it matter. He flushed the cache in his head and tried again.

Red Hen had been told that nostalgia was fascist thinking. He finally found the item he had been sent for. He reached his right hand out toward the crowded desk and pulled a lone sheet of paper up and held it between both hands, his fingers giving him the wonderful haptic feedback he craved and longed for. It was the fax and all that the company wanted was on it. Everything went into this supercomputer and everything was sent back to Network.

Red Hen was suddenly hooked into the Network's line and the feed was moving fast as always. It flashed before his eyes (just two flat, rectangular steel plates; the eyes of its ``sensor head'')\footnote{Red Hen was designed by United States Heavy Industries and Research. Basically OmniCorp Consumer Products so it was little wonder the design team had an affinity for ``Cain-RoboCop or RoboCop 2'' from the film \textit{RoboCop 2}. Red Hen's body was made to resemble the B1-Battle Droid from the Disney franchise we don't name albeit made to look even more human. This was so that it could wear human gear and put flesh humans more at ease. It left things to be desired but Red Hen was better off looking this way than the minigun equipped agile waling-tank the designers originally had in mind.} and the screens that reflected his mind to itself replayed for him the news of the day that mattered to him or was suppose to matter to him in any case. Operation Just Cause III; little resistance in Northern Mexico. A besieged city-state is what they were calling Mexico City. Who would have guessed? McNamara's Boys (Red Hen's unit) and at the tone\dots

Red Hen jolted and made fast out of there making across Red Mountain toward McNamara Hut. Snow getting deeper and the remote operators were well aware of all the warnings piling up in the associated log files but they weren't concerned because Red Hen had been designed for this and everything else. Red Hen was a solider supercomputer that ran hot now and then so being cold did him some good. Along the way supplies had been airdropped and the equipment looked like an amazing array of new Apple products but with military colors suited for the location. The crates snow white and hidden from anyone but Red Hen who had the sensors needed to find it.

He sat down next to the crates and unloaded the contents of each carefully. Weapons and ammo and a microSD card to slide into his mind. We became concerned when he hung for a tad too long studying it but worse hiccups have happened before.

What I saw and read in the logs and have thought about as I am sure Red Hen thinks about since is, well, something I'll always remember and hope never to forget. Red Hen will remember his way so perhaps asking him one day would be worth it but nevertheless before this sentence is snapped like an icicle according to all the data and confirmed (in my mind at least) by the visual data it was as cold as one that night. The operators recall wanting to see Red Hen's breathe or wishing there was some mechanism that could be employed to allow for it. Red Hen looked up and the Moon was almost silver and so little clouds in a blue black night it was truly wonderful. It was an \textit{Owl Moon} sky taken directly from that children's book truly. It was as if Red Hen had eyes, I swear and he tilted his sensor head slightly to catch the General Atomics MQ-1 Predator moving at a pace of leisure. It was at this point we lost any real remote control we had over it and it did go true rouge but stayed on mission as far as we could tell up to that point. We hadn't any real idea how far the MQ-1 was as we were shocked enough to see an MQ-1 flying at all and we knew it wasn't ours or hadn't been for a long time. This was Occupied Territory of the United States (OTUS) and had been for as long as any of us operators could remember. Red Hen judged it wasn't in too much danger of the Zuni rocket that had been modified and attached to the MQ-1 (we learned all about it much later) and decided to open its sensor head and scan the fax it had been handling. It wasn't any surprise why the designers had added this screen to Red Hen's head to be thrust open and closed as that was the Hollywood slop they were taught on. In any case, it allowed us to actually scan the fax for upload and to glean its physical proprieties; truly a marvelous thing. Red Hen had enough time for this and kept watch on the MQ-1 as it sailed across the chilly night sky and the silver Moon in a holding pattern. By God, it was in a holding pattern we couldn't comprehend. We all watched it over and over again. It was as if Red Hen were framing us the shots of a movie so serene. Its onboard cameras had never recorded like that. Network was abuzz. Why had Red Hen waited to physically scan the fax now? We didn't know but surely all understand we were doing our best at the time to report it via Network and even hardline. We learned later that Wider Network and Red Hen had been pinging and we surmised whatever pinged Red Hen pinged him for this. Red Hen's thinking (at least then) was always available to us but it was moving like an old fashioned ticker tape we ignored being so consumed by our own screens and monitors. His thinking was right there and hadn't been scrambled. Looking back at that tape or scroll of thought we saw that Red Hen knew there was a page missing from the fax so he sucked back in his scan screen and shut his sensor head and made his way back toward the cabin looking like MacArthur wading ashore.

The MQ-1 was monitoring it all. Red Hen showed no real concern about that although he had armed himself/itself with the equipment we had thought would be needless. All painted snow white:

\begin{tabbing}
\= \qquad \= \qquad \= \\
\> MicroUzi \\
\> \> M9 \\
\> \> \> M4 carbine \+ \+ \+ \\
\end{tabbing}

Red Hen was thinking he hadn't been armed before opening and equipping what was in the crates. Before he had set out again for the cabin He studyed the sightings of the M9 and pulled the slide back to see the bullet nestled in the chamber. He holstered it and checked both the carbine and the MicroUzi. He decicded on the MicroUzi. The MQ-1 kept pattern as Red Hen got closer to the cabin. 

I can say with great confidence after having reviewed the data that the steel plates of his sensor head protecting the scan screen were cooler than the logs had ever recorded before. The Moon was the only light and it illuminated the cabin eerily when it came within sight of the cameras. Nothing moved just as nothing moved before he had arrived earlier. Yet Red Hen stuided the cabin for a long time and there wasn't much thinking going on from what we could tell. We did notice, again in the logs and again after the fact, that its grib on the MircoUzi was tighting beyond the standard programmed.

Red Hen and by extention we remote operators saw things we hadn't the first go around. Red Hen wanting to put a few rounds into his sensor head made more sense after what we all saw. The thought has been classifed since but it is worth repeating, I suppose. By this time Network was informed enough to have dispatched another strike team but what made this one different than the one that had been there before Red Hen had initially arrived was human advisors accompanying the bots that were Red Hen's make and model mostly. Some older models but things were moving so fast these days it was hard to replace the older ones fast enough.

The first strike team had done their job well and with no humans present. This was an American first. Big American History if we're being totally honest and given this report is for the Network I wouldn't lie, I swear to God and our Lord and Savior Jesus Christ. The first team had been sent from the \textit{USS Jesus and Jenny} out in the Pacific. Long flight but that just added to the historicity of it. Whereas Red Hen arrived via airdrop. Space Force handled his insertion whereas the Navy was tasked with the first. And the Navy only started their flight when Red Hen was close enough; it had been hiking for a few days. Just the way it was. Navy boys said they'd get in and out without alerting a mouse. They pretty much did, I suppose but the MQ-1 had us wondering if they really had.

\end{document}

