% mentioned p.9
\documentclass[13pt|draft]{report}

% mentioned of p.226 of Lamport, 2ed
\ttfamily
\title{Red Hen's Last Adventure or \em Hypercomputers for Superpowers in Trouble}

\begin{document}

\maketitle
% https://tex.stackexchange.com/questions/319875/how-to-make-dedication-page-and-move-words-to-the-middle
\clearpage
\begin{center}
    \thispagestyle{empty}
    \vspace*{\fill}
    For John Sr and John Jr and Rocco
    \vspace*{\fill}
\end{center}
\clearpage

\begin{quote}
{\em\small{The fax. False Battle of Acapulco. Aspen nights and drones above. True Battle of Acapulco. Missile strike and firefight.}}
\end{quote} 

\section*{} % this is a hack, also - for a blank page?

Red Hen looked down at the desk contemplating that, had it been armed, he'd have unloaded a few rounds into his own sensor head, but he knew it was pointless and he began to wonder why it was programmed at all to allow such thoughts and that thought looped for awhile and meantime he's looking like Martin Riggs staring at the face of his cocked pistol and feeling like a pustule.

The desk was assaulted and covered in the wild red blood of the General which was soaking into the ornate rug beneath. Why was he here again? Red Hen thought he'd like to know and even though it was equipped with NPUs and CPUs and TPUs and enough yottabytes of memory to store humanity's Hollywood movie collection too many times over it still never really understood why it acted the way a human might and mostly forgot why it was doing what it was doing and for whatever reason and thank the Lord it was supposed to work that way. We flushed various caches in his head and tried again.

Red Hen found the physical media he had been sent for. He rolled over the corpse and extracted the fax, his fingers giving us wonderful haptic feedback and making us feel alive as it gracelessly freed said media from the x-crossed arms of the General who had been hugging the piece of paper to his chest as if it were his dead infant. The fax simply was a list, in no particular order, of names and accommodations of each VIP to the upcoming Peace Conference at Hartford, CT. Everything Red Hen looked at went into its hypercomputer and everything was sent back to Network. He optically scanned a scan of a fax which was digitized and retransmitted. We hadn't yet figured why the Party had started using fax machines but Langley was guessing something something audio-frequency tones? Red Hen flattened the paper working his twenty fingers over the raised parts which resembled the mountains outside but with nightmarishly jagged peaks. Red Hen studied the fax, feeling it all over for the benefit of our hands before carefully folding it into a neat square.

Network abruptly brought the news flash to the foreground. Red Hen was constantly hooked into Network's feed. The feed was one among many many many trillions of values evaluated at once. It played out before his ``eyes'' (two flat, rectangular steel plates airbrushed permafrost; the eyes of its ``sensor head'')\footnote{Red Hen was designed by United States Heavy Industries and Research which was more or less ``OmniCorp Consumer Products'' so it was little wonder the design team had an affinity for ``Robocane'' or ``RoboCop 2'' from the motion picture \textit{RoboCop 2} (1990). Red Hen's body was made to resemble the B1-Battle Droid from the Disney franchise Kershner worked on in 1980 albeit made to look even more human. This was so that it could wear U.S. Armed Forces Combat Capabilities Development Command Soldier Center Clothing Systems to keep Advisors at ease and happy. It left things to be desired but Red Hen was better off looking this way than the minigun equipped agile walking-tank \textit{some} designers originally had in mind.} that reflected his mind to itself the news that mattered to him or was supposed to matter to him: Operation Just Cause III---little resistance in Northern Mexico. A besieged city-state is what they were calling Mexico City. Who would have guessed that ``McNamara's Boys'', Red Hen's unit, were embedded with Mexican nationals and at the tone Acapulco falls and God Bless America!

Later, while I was reviewing the logs in my terminal, I saw the force fed memory of that city's liberation: The M134 minigun armed bot Fireball Roberts with a persona programmed in that made it behave like Blain Cooper from \textit{Predator} (1987) bear hugging its Advisor and at times during the battle complaining that rebels were dug in like an Alabama tick; Purple Turkey, communications bot, grabbing both shoulders of its Advisor, pressing its steel head against human flesh and rejoicing. Deep Goose, the medic bot, having deep thoughts (most of which have been classified) while recording the Pacific below as its bird glided over the water with the speed boats making it all look like a miniature D-Day. This latter recording being the only real true honest information. Something seemed unreal about everything else, I swear. I felt something in my gut about that news flash. Some things are just too good to be true, Lord knows.

Into the night Red Hen began hiking across Red Mountain toward McNamara Hut. Extract was there and we wanted to take a stand and raze the absurd and ahistorical museum the Party had made out of Robert McNamara's Hut. Snow kept getting deeper and we remote Advisors were well aware of all the warnings piling up in the associated log files but we weren't concerned. Red Hen had been designed for this and everything else. Lord knows the logs were many and we remote Advisors so few. Red Hen was our soldier toy/boy and we loved him, I swear. He  ran hot now and then so being cold did him some good. Halfway toward the Hut he found the supply drop. He knelt down and unloaded the contents of each crate carefully. Weapons and ammo and a microSD card to slide into his mind. We became concerned when he hung for a tad too long studying the microSD card but worse hangs had happened before.

What I saw and remember and watch and re-watch and read and re-read in the logs and have thought about since as I am sure Red Hen thinks about is, well, something I hope never to forget. Most Advisors recall wanting to see Red Hen's breath or wishing there was some such mechanism that could allow for the release of harmless vapor as silly as it sounds but imagine it and it makes sense. It was as if Red Hen had eyes, I swear, and as he bent his sensor head slightly toward the moon he caught the General Atomics MQ-1 Predator moving at a pace of leisure across the black-blue night with shafts of white moonlight revealing its Zuni missile. Yes, by God, a Zuni! It was at this point we lost any control we had over it/him/Red Hen. We hadn't any idea how near or far the MQ-1 was as we were in a state of shock since just seeing an MQ-1 flying at all and after so many years and we knew it wasn't ours or hadn't been for some time. This was Occupied Territory of the United States. Subverts on Reservations that flipped are calling it the ``Long Outwaiting'' this cold now hot later war we are fighting. Red Hen judged it wasn't in too much danger of the drone and decided to open its sensor head and scan the fax it had been handling, finally gleaning its physical proprieties. Red Hen did this and kept watch on the MQ-1 as it sailed in the sea above in a holding pattern we couldn't comprehend. We all watched it over and over again. It was as if Red Hen were framing us the shots of a movie so serene. Its onboard cameras had never recorded anything like it. Not that I'd ever seen. Why had Red Hen waited to physically scan the fax? We didn't know but surely all understand we were doing our level best at the time to report it via Network and even hard line. We learned later that Red Hen had been pinging the open internet and we surmised whatever pinged Red Hen pinged him for this. Red Hen's thinking (at least then) was always available to us but it was moving like an old fashioned ticker tape we ignored being so consumed by our own screens and monitors. His thinking was right there and hadn't been scrambled.  Red Hen finally gleaned the sub-properties, the molecular metadata of the fax which revealed its true message which in turn revealed there was a page missing and so it sucked in its scan screen and shut its sensor head plates and ramrod up it stood. We'd figured the guns would have been needless so we had had fun. Not a great idea in hindsight but we'd had such success lately with Red Hen's model we sent old firearms, all with a snow white finish:


\begin{tabbing}
\= \qquad \= \qquad \= \\
\> \> \> Military Armament Corporation Model 10 ``M10'' / ``MAC-10'' \\
\> \> \> Beretta M9 \\
\end{tabbing}

Before he had set out again for the cabin Red Hen studied the sightings of the M9 (just like Martin Riggs!) and pulled the slide back showing us a bullet nestled in the chamber. He holstered the M9 while he had been checking and loading both the M7 and the M10. He had extended his two spare arms we hadn't been happier to have had him equipped with as the feature is optional and Gorman lacked them and we believe this is part of the reason (besides the Zuni) that Gorman lost the later battle. Red Hen field stripped the ``MAC-10'' and checked every detail, working 15 fingers over it.

Red Hen was making its own decisions and it wanted page two of that fax. The MQ-1 kept pattern as Red Hen returned to the cabin.

I can say with great confidence after having reviewed the data that the steel plates of his sensor head were colder than the logs had ever recorded them being before. The moon's white light illuminated the cabin when it came within sight of his cameras. Nothing moved just as nothing moved before he had arrived earlier besides the wind pushing a shattered window's drapes, and a small piece of that window's glass falling and twinkling as it landed in the snow; small things like that. Red Hen studied the cabin for a long time. We did notice in the logs after it all that its grip on the M10 was tightening beyond the standard programmed.

Red Hen, and by extension we remote Advisors, saw things we hadn't the first go around. Red Hen wanting to put a few rounds into his sensor head made more sense. The thought has been classified. By this time Network was informed enough to have dispatched another Strike Team. This Third Team was different in that human Advisors were accompanying the bots of Red Hen's make and model.

The First Team had done their job well and with no human Advisors present, either remotely or locally. This was an American first. Big American History if we're being totally honest and given this report is for Network I wouldn't lie, I swear to God and our Lord and Savior Jesus Christ. The First Team had been sent from the amphibious assault ship \textit{USS Calgary} up in the Arctic. That just added to the historicity of it. Space Force handled Red Hen's insertion with their newest jet-black drop capsule. Navy had only sent their bots when Red Hen was within twenty miles. Red Hen had been hiking for a few days.

Between coffees and Coca-Colas we remote Advisors would watch the feed and it was a calming atmospheric viewing experience so much akin to those ambient TV streams with drones doing all the impressive shots. Now it's our bots with so many cameras on board I have to check the spec but the viewing is almost immersive. Add the actual mini-drone Red Hen is equipped with but lost on this outing: an Advisor had taken manual control of it for a wide, sweeping shot he claimed was for his wife who's mother's mother's mother or some such had been a resident of CO back before most of it was occupied. Red Hen had deployed the mini-drone to map terrain ahead and evaluate best measures of success. It was a blow to lose that mini-drone which would have been helpful later.

Red Hen had been deposited directly into the much damaged Eisenhower Tunnel. The drop capsule doors were damaged on entry so Red Hen had to force them. I won't lie. Red Hen looked very Hollywood Army Hero in the Extended Cold Weather Clothing System. Even his additional (optional) ligaments were dressed and protected as if human flesh was underneath it all. Onto I-70 and eventually up and over Mount of the Holy Cross. Imagine this: an unarmed, mini-droneless bot wading through the twisting and descending road and snow and then back up ascending  the mountain's earth and seeing old checkpoints and forgotten APCs and cars from the PRC with remnants of long ago violence visible here and there now and then. Red Hen made for higher rocks. Sometimes just hiking straight up the body of the cross. Behind him that old engineering marvel twisting and turning and receding. Many Advisors were wishing they could feel the air Red Hen felt on its sensor head and not just the few objects haptic feedback was permitted for transmit over Network. Cost savings is the claim.

Just the way it was. Navy boys said the bots' work would go undetected, unobserved. That MQ-1 had us wondering if they really had.

Red Hen, almost as if by inspiration, stood up from his prone position observing the cabin and walked slowly up to the front door. Nothing had been disturbed. The three sedans on the winding drive still contained their dead occupants. The First Team's bots had riddled the cars and we made a note about that. Seemed needless. Excessive.

The cabin's windows had been blown away by gun fire and pockmarks from bullets were everywhere. Red Hen gently pushed open each door with the M10 framing it all like an art house movie. The First Team searched and destroyed but was ordered to take nothing. Navy bots deliberately hid the second page of the fax under the corpse of the Chinese General's daughter. I've read reports from the Navy about this and one bot did this all ``sub-rosa'' they claim. Perhaps all the bots collectively engaged in the deception? Parts of the report are classified.

Red Hen began checking every body, scanning every face. The death masks were 3-D printed as the bits and bytes made their way through Network. Ours and someone else's. I can't recall a bot ever doing this. We wanted Red Hen to check on the MQ-1 and we issued orders to that effect but no pingback, no ack, yet his cameras broadcast back live everything it saw.

Red Hen turned over that little girl and hung for a long time. The Third Team's helicopter was inbound and Network was sure the Party was hijacking Red Hen with the MQ-1 but the Third Team, for whatever reason, wasn't told about it so when they hit the ground the MQ-1 fired off the Zuni and its aim was true. It was a real shit show by then and Network had one line:

\begin{tabbing}
\= \qquad \= \qquad \= \qquad \= \\
\> \> \> \> \large We say again: kill Red Hen.
\end{tabbing}

The Zuni had damaged but not disabled the bot Gorman and killed an Advisor and the bird and the human flying it. The bot Vasquez and its Advisor were unharmed. They let the mangled Gorman take point.

Red Hen had been kneeling in the guts and blood of that kid and was ignoring the fax sheet papier-mâchéd onto her body. It just had this little girl's face pressed against its scan screen which was a pinscreen reversed and seemingly swallowing her face. Red Hen held her tightly by the small of her back, arching her. After scanning her face, he placed her on the floor and carefully removed the plastered fax from her body and set it aside. After this was done he respectfully placed the child next to her father. Then it picked up page two and began the touching ritual as it had done for page one but now our hands weren't feeling it. Some kind of morse code but only for Red Hen's make and model's hands? Langley's still working it out. Red Hen proceeded to physically scan this page also to get the entire story. McNamara's Boys had been massacred. Fireball Roberts, Purple Turkey, Deep Goose; all more or less disabled. For how many Advisors went in too few came out. It was so horrible to see those images all over Network of Americans getting managled indiscriminatly. The Chinese People's Navy had deployed their latest models to defend Mexican rebel positions. The Party keeps touting ``Edgar Snow''---the moniker given their knockoff of Red Hen.

The true Battle of Acapulco had some beautiful moments, I can't lie. We'll use what we learned I have no doubts. I recount it here only because the unreality of it makes me feel the need. After hitting the beach from the air with the cover of hellfires and sidewinders that make the Zuni look like that piece of shit it was but, God rest our boys souls, the Zuni did take out a good chunk of the ``USS Zippo''. And suddenly Fireball Roberts is Animal Mother from \textit{Full Metal Jacket} (1987) and he's unloading his M134 against anything with a pulse and anything lifeless too; everything was asymmetrically splattered. ``...electric word, life, it means forever...'' was murmured right before Purple Turkey bought the virtual farm and had its sensor head blown away by a Mexican sniper who subsequently became rather famous for the feat. There was a moment, Lord, that was lifted from \textit{Saving Private Ryan} (1998); the bots reworked that scene with the Jew named Fish from Brooklyn and the Nazi piercing his poor Jewish heart with the knife but the bots deviated from the source material, of course. Deep Goose and this Chinese knockoff crash through and there's some Mexican kids huddled all scared shitless, I swear to Jesus, like I've never seen. The bots were hand-to-hand at this point and to calm the children began a shadowboxing routine that was almost incomprehensible but they did manage to calm the children a tad. The bots finally drew their sidearms and both raised their index fingers to where on their sensor head the lips would be and as if saying ``sssssshhhhhh, everything will be alright'' they proceeded outside both locked on to the other's sensor head and Deep Goose lost his to a Chinese high velocity round.

That's what Red Hen was seeing and relaying to Network as Gorman's dispatched mini-drone circled above Red Hen in the cabin and recorded. All of Red Hen's thoughts were instantly classified. It slide the microSD into its slot and all us remote Advisors were in an uproar as that microSD contained new mission parameters and we knew that the MQ-1 was getting it all in one form or another. I had an outburst of joy when we heard the sudden whistle and snap of automatic fire.

Gorman instantly became an American hero to us all. We were getting the action from many angles and with Red Hen becoming such a talented cinematographer it made for amazing viewing. Gorman's aim wasn't true, however. The Zuni had damaged enough to make Red Hen aware just in time to counter and avoid much of its own damage. Red Hen was able to grab its ``MAC-10'' and squeeze off a few rounds that struck Gorman's standard issue rifle and tore into him at the right spots and perhaps even weakened one of its sensor head's ``eyes''. We later discovered someone had stocked high velocity ammo for the M10 in the crate. Logs indicate it was an act of love. Gorman's reaction happened fast: rushing Red Hen, grabbing him by the neck and shoving him against the wall to begin punching at the speed of anime directly at Red Hen's torso, motivated by the slightest sight of any black as motor oil blood, which ran through the microfiber tubes that were their veins. Red Hen began its own punching focused on Gorman's left face plate. He got in many good licks and dented the damn thing to the point he was able to wedge one of his upper right hand's fingers underneath the corrugated wound and with his upper arm's left hand he drew his white M9 and fired away at the innards of Gorman's ``skull''. 

Most of the vital workings of the bot aren't located in its head but enough matter and Gorman was damaged, his backups weren't working as they should have been. It was at this point, as you know as well as I from the logs, that Red Hen stood up and Red Hen's cameras were mostly offline so we didn't get his POV. Vasquez and her Advisor were unloading everything heavy they had. Red Hen was undoubtedly being splintered apart with bullet hit squibs bursting. The footage from Vasquez did show him in a very Hollywood position of death: on his knees in a pool of his own bot guts and black engine oil. Almost Christlike? No! Thích Quảng Đức-like, my God! The Advisor gathered up the microSD and faithfully crushed it.

Vasquez looked down at Red Hen and hung for a long time. Her Advisor was scrambling for extract and was getting confused with each passing order not acknowledged. Vasquez looked up at the cabin's ceiling, blown away by some previous munition. She saw the MQ-1 with the white moon behind it and it was as if a lamp enclosed in crystal stashed away in a niche suddenly became lit with a starlike brilliance within her sensor head plate, as seen from her Advisor's helmet's cameras. Vasquez raised her sidearm and her aim was true.\\
\end{document}

