\pdfvariable suppressoptionalinfo 512\relax
\documentclass{muratcan_cv}
\usepackage{fontspec}
\setmonofont{CommitMono}

\setname{Ryan Joseph Patrick}{Casalino}
\setaddress{Seattle, WA USA}
\setmobile{917.282.7506}
\setmail{ryan.casalino@gmail.com}
\setposition{Programmer}
\setlinkedinaccount{https://www.linkedin.com/in/ryan-casalino-b2ba55290/}
\setgithubaccount{https://www.github.com/rjpcasalino}
%\setthemecolor{YellowOrange}
\setthemecolor{Red}

\begin{document}
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
I am a largely self-taught programmer with proven ability. I am comfortable with a variety of programming languages and am familiar with modern software paradigms.
I enjoy working with UNIX-like operating systems NixOS and OpenBSD. I strive to write clean code and understand systems. If given an ambiguous problem I can solve it. But I'm also a team player and I'm not afraid to ask for help. I am a life long learner with a growth mindset and avid reader. I have a passion for technology and a desire to help people.
}
%
\section{Experience}
    %
    \datedexperience{Liaison Technologies}{2015 - 2017 / Atlanta, GA}
    \mbox { \scshape \hspace{1.2em} \tiny{\texttt{Liaison Technologies allowed organizations
     to meet their toughest data challenges while building a robust data-centric foundation.}}}\\
    \explanation{Software Programmer}
    \indent \indent \begin{minipage}{0.96\linewidth} \footnotesize
     At Liaison I contributed to Node.js RESTful APIs built with Hapi.js for a variety of internal and customer-facing services. Working on a cross-functional team that spanned oceans we produced MVPs in an agile environment. I was also responsible for maintenance of various front end and back end systems.
    \end{minipage} \\[0.1cm]\\
    %
    \datedexperience{Merchant-e Solutions}{2017 / Atlanta, GA}
    \mbox { \scshape \hspace{1.2em} \tiny{\texttt{Merchant-e makes payment processing simple.}}}\\
    \explanation{Software Programmer}
    \indent \indent \begin{minipage}{0.96\linewidth} \footnotesize
     While with Merchant-e I delivered a Node.js database connection CLI for an Oracle database to replace an aging and arcane Java-based solution. I supported Apache and nginx server upgrades and maintenance for a variety of front end applications ranging from the POS UI to the company's marketing website. I also mentored junior developers and helped them with their projects. Finally, I was able to introduce the company to the benefits of using Docker for development and production environments.
    \end{minipage} \\[0.1cm]\\
    %
    \datedexperience{Various Startups}{2017 - 2020 / Seattle, WA}
    \mbox { \scshape \hspace{1.2em} \tiny{GawkBox, React Mobile, Contract roles elsewhere}}\\
    \explanation{Software Programmer}
    \indent \indent \begin{minipage}{0.96\linewidth} \footnotesize
            During this time I first worked at "GawkBox"—a startup whose mission was to help monetize streamer content. I owned the rewrite of their authentication API replacing a hastily written Node.js API with Go resulting in reduced code complexity. I also stood up a MySQL DB to work in conjunction with this API. I introduced Vue.js for v2 of their front end replacing a poorly supported Sails.js implementation. I enhanced the login/authentication experience for users of the platform while adding new features. Next, working for "React Mobile" I oversaw and maintained a Ruby based queue system for the company's "Panic Button" solution ensuring both up-time and availability. I developed features for an Electron based front end that allowed users to remotely manage wireless beacons. One such feature was the ability to remotely update the firmware of said beacons. I also oversaw aspects of the company's AWS infrastructure.
    \end{minipage} \\[0.1cm]\\
    %
    \datedexperience{Sinch}{2020 - 2022 / Bothell, WA}
    \mbox { \scshape \hspace{1.2em} \tiny{\texttt{Sinch powers meaningful conversations at scale across
    messaging, voice, and email to help businesses deliver personalized experiences.}}}\\
    \explanation{Senior Software Programmer}
    \indent \indent \begin{minipage}{0.96\linewidth} \footnotesize
     I contributed to the creation of personalized SMS and RCS messages with a Ruby proxy service driving Adobe After Effects. I maintained a content management system written in an obscure Ruby framework and documented arcane processes within said system.
    \end{minipage} \\[0.1cm]\\
    %
    \datedexperience{Ad Hoc}{2022 - Now / Seattle, WA}
    \mbox { \scshape \hspace{1.2em} \tiny{Ad Hoc empowers organizations to deliver digital
    services that promote the general welfare.}}\\
    \explanation{Software Programmer III}
    \indent \indent \begin{minipage}{0.96\linewidth} \footnotesize
     I help maintain and ship new features for the Medicare.gov Plan Finder application. This work includes owning portions of both plan and drug data ETL processes which involves myriad scripts written in three different languages. I also provide support for the authentication experience for Medicare and Medicaid beneficiaries. I assist in maintaining Plan Finder's IaC using Terraform and write documentation for Plan Finder's internal documentation website. I help support the company's internal recruiting tool ("People App") fulfilling feature development and maintenance requests. I've created CLI tools for internal operations to make the jobs of both Software Engineers and Product Managers easier. These CLI tools allow for connection to government VPN and allow stakeholders to query databases securely, query the status of our systems in general, and perform various cloud operations. I also preform code reviews and evaluate the "homework" submissions of job candidates while assisting my peers in debugging issues with the online evaluation environment.
    \end{minipage} \\[0.1cm]\\
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{ Go | Python | Ruby | JavaScript | Bash | Perl | Terraform | SQL }}
    \newcommand{\skilltwo}{\createskill{Cloud}{ Amazon Web Services | Google Cloud Platform }}
    \newcommand{\skillthree}{\createskill{Software Development}{ Agile Methodology | DevOps Lifecycles }}
    \newcommand{\skillfour}{\createskill{Software Tools}{ git | gRPC | JSON | XML | Protobufs | Docker | *nix }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%
%Education
\section{Education} 
    \datedexperience{School of the Art Institute of Chicago}{2006 - 2011}
    \explanation{BFA with emphasis on writing}
    \datedexperience{General Assembly (Atlanta) }{Spring 2015}
    \explanation{code boot camp}
%
% Extra
\section{Extra}
    \newcommand{\extraone}{%
     NixOS and OpenBSD enthusiast and user.
    }
    \newcommand{\extratwo}{%
     Avid blogger and manual page reader.
    }
    \newcommand{\extrathree}{%
     Open Source contributor. IPv6 advocate. Raspberry Pi tinkerer.
    }
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    %
    \createbullets{\listofextras}
%
%Footnote (removed for now)
%\createfootnote
\end{document}
